---
title: beef_metabolomics_maplet_v1_cmerge_buffer_removed
output:
  html_document:
    toc: true
    toc_float: TRUE
    
params:
  D: NA
---

```{r echo=F}
# default chunk options
knitr::opts_chunk$set(warning=F,echo=F,results='hide',message=F)
```

```{r}
# load libraries
library(maplet)

```

```{r}
r <- metadata(D)$results
```

# Output
# Data-Cleanup
## Missingness
Missigness before removing buffer

### plots_missingness
*Log text:*<br/>missingness plots, missing values: 14853 out of 113400 (13.10%)

```{r}
r[[4]]$output
```


Missingness after removing buffer

### plots_missingness
*Log text:*<br/>missingness plots, missing values: 10227 out of 90720 (11.27%)

```{r}
r[[6]]$output
```


### pre_filter_missingness
*Log text:*<br/>features filtered, 50.00%, 39 of 630 removed


Missingness after filtering metabolites with more than 50% missing values per group

### plots_missingness
*Log text:*<br/>missingness plots, missing values: 6331 out of 85104 (7.44%)

```{r}
r[[9]]$output
```


### plots_sample_boxplot
*Log text:*<br/>sample boxplot, aes: color=Buffer

```{r}
r[[10]]$output
```


### plots_sample_boxplot
*Log text:*<br/>sample boxplot, aes: color=tissue

```{r}
r[[11]]$output
```


### pre_norm_quot
*Log text:*<br/>quotient normalization based on 36 reference samples and 511 variables: ~

*Log text:*<br/>quotient normalization based on 36 reference samples and 511 variables: Buffer == "80% Meth + 20% H2O"


### plots_dilution_factor
*Log text:*<br/>dilution factor plot, 'Buffer'

```{r}
r[[13]]$output
```


### plots_sample_boxplot
*Log text:*<br/>sample boxplot, aes: color=Buffer

```{r}
r[[14]]$output
```


### pre_trans_log
*Log text:*<br/>log2.000000


### plots_sample_boxplot
*Log text:*<br/>sample boxplot, aes: color=Buffer

```{r}
r[[16]]$output
```


### pre_outlier_detection_univariate
*Log text:*<br/>flagged 0 univariate outliers


### reporting_data
*Log text:*<br/>Dataset info: 144 samples, 591 features; 25 sample annotation fields, 10 feature annotation fields

### write_se_xls
*Log text:*<br/>Data exported to Excel file 'PreprocessedData.xlsx'


# Global Statistics
## plots_umap
*Log text:*<br/>UMAP, label_col: , aes: color=Buffer, size=2.5

```{r}
r[[21]]$output
```


## plots_heatmap
*Log text:*<br/>Heatmap of assay data.

```{r}
r[[22]]$output
```


## plots_umap
*Log text:*<br/>UMAP, label_col: , aes: color=tissue, size=2.5

```{r}
r[[23]]$output
```


## plots_heatmap
*Log text:*<br/>Heatmap of assay data.

```{r}
r[[24]]$output
```


## plots_pca
*Log text:*<br/>PCA, scores, label_col: , aes: color=Buffer, shape=tissue, size=2.5

```{r}
r[[25]]$output
```


## Buffer analysis
### stats_univ_lm
*Log text:*<br/>univariate lm, ~Buffer

```{r results='asis'}
# extract result table
df<-r[[27]]$output$table
# add feature names
rd <- rowData(D)
df <- cbind(name=as.data.frame(rd)$name[match(df$var, rownames(rd))], df) %>%
  dplyr::arrange(p.value)
# subset large data frames
if(nrow(df) > 1000) df <- df[1:1000, ]
# output
DT::datatable(df, rownames = FALSE, filter = "top", options = list(pageLength = 20, lengthMenu = c(10*(2^(0:3)), nrow(df)), autoWidth = TRUE, width = 1200, dom = "Bitlrp", buttons = c("copy", "csv", "excel", "pdf", "print")), class = "cell-border stripe", extensions = "Buttons")  %>% DT::formatStyle(columns = c(1:ncol(df)), fontSize = "80%", target= "row", lineHeight="80%")
```


### post_multtest
*Log text:*<br/>Multiple testing correction of 'Buffer met' using 'BH'


### reporting_stats
*Log text:*<br/>'Buffer met' info

Samples:
50% Meth + 50% H2O: 36, 50% Meth + 50% PBS: 36, 80% Meth + 20% H2O: 36, 80% Meth + 20% PBS: 36 /// features: p.adj < 0.05, 125 of 591

### write_stats
*Log text:*<br/>Exported sheets 'Buffer met' to Excel file 'BufferAnalysis.xlsx'


### plots_pval_hist
*Log text:*<br/>P-value histograms for Buffer met

```{r}
r[[31]]$output
```


### plots_box_scatter
*Log text:*<br/>Feature 

```{r ,fig.width=7.000000,fig.height=141.346528}
r[[32]]$output
```


## Tissue analysis
### stats_univ_lm
*Log text:*<br/>univariate lm, ~tissue

```{r results='asis'}
# extract result table
df<-r[[34]]$output$table
# add feature names
rd <- rowData(D)
df <- cbind(name=as.data.frame(rd)$name[match(df$var, rownames(rd))], df) %>%
  dplyr::arrange(p.value)
# subset large data frames
if(nrow(df) > 1000) df <- df[1:1000, ]
# output
DT::datatable(df, rownames = FALSE, filter = "top", options = list(pageLength = 20, lengthMenu = c(10*(2^(0:3)), nrow(df)), autoWidth = TRUE, width = 1200, dom = "Bitlrp", buttons = c("copy", "csv", "excel", "pdf", "print")), class = "cell-border stripe", extensions = "Buttons")  %>% DT::formatStyle(columns = c(1:ncol(df)), fontSize = "80%", target= "row", lineHeight="80%")
```


### post_multtest
*Log text:*<br/>Multiple testing correction of 'Tissue met' using 'BH'


### reporting_stats
*Log text:*<br/>'Tissue met' info

Samples:
fat: 48, liver: 48, muscle: 48 /// features: p.adj < 0.05, 360 of 591

### write_stats
*Log text:*<br/>Exported sheets 'Buffer met, Tissue met' to Excel file 'TissueAnalysis.xlsx'


### plots_pval_hist
*Log text:*<br/>P-value histograms for Tissue met

```{r}
r[[38]]$output
```


### plots_box_scatter
*Log text:*<br/>Feature 

```{r ,fig.width=7.000000,fig.height=402.402778}
r[[39]]$output
```


## Multiple Statistics Heatmap
### plots_multstats_heatmap
*Log text:*<br/>Pheatmap of stat results.
 Colors represent (sign(statistic) * -log10(p.adj)))

```{r}
r[[41]]$output
```


## Result Comparison
### plots_stats_compare
*Log text:*<br/>comparison plot between 'Buffer met' and 'Tissue met'

```{r}
r[[43]]$output
```


